# Set up

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
library(here)
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

# --- figure making --- #
# library(extrafont)
library(ggbrace)
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

# --- table making --- #
library(flextable)
library(ftExtra)
library(officer)
library(officedown)
library(modelsummary)
```

# figure and table set up

```{r}
theme_figure <-
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank(),
    text = element_text(family = "Times New Roman")
  )

theme_dist <-
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    text = element_text(family = "Times New Roman")
  )

set_flextable_defaults(
  font.family = "Times New Roman"
)
```


# Read Field Data

```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
# === plot-level field data set  === #
field_plot_sf <-
  here("Data/for_writing/sample_field_plot_sf.rds") %>%
  readRDS()

# === subplot-level field data set  === #
field_subplot_sf <-
  here("Data/for_writing/sample_field_subplot_sf.rds") %>%
  readRDS()

# === cell-level field data set  === #
field_cell_sf <-
  here("Data/for_writing/sample_field_cell_sf.rds") %>%
  readRDS()
```


# Illustrative Examples of MB Yield Response Curves (Figure 2)

```{r}
# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- MB function --- #
gen_yield_MB <- function(ymax, alpha, beta, N) {
  yield <- ymax * (1 - exp(alpha + beta * N))
  return(yield)
}

# --- extract sites that have wide range of true optimal N --- #
get_rows_optN <- function(data, value, range) {
  res <- data %>%
    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))] %>%
    .[, group := value]
}

prep_coef_dt <-
  field_cell_sf %>%
  data.table() %>%
  .[sim == 1, .(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]

set.seed(34864)

coef_dt <-
  lapply(
    c(0.01, 0.25, 0.5, 0.75, 0.99),
    function(x) get_rows_optN(data = prep_coef_dt, value = x, range = .0005)
  ) %>%
  bind_rows() %>%
  # --- select one site from each group --- #
  .[, .SD[sample(.N, size = 1)], by = group]

seq_N <-
  seq(min(coef_dt[, opt_N]) - 50, max(coef_dt[, opt_N]) + 100, by = 1) %>%
  round()

res_y_dt <-
  coef_dt %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = group] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)] %>%
  .[, opt_N := round(opt_N)] %>%
  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
  .[, variable := case_when(
    variable == "det_yield" ~ "Yield",
    variable == "yield" ~ "Yield including errors"
  )] %>%
  .[, group := case_when(
    group == 0.01 ~ "site 1",
    group == 0.25 ~ "site 2",
    group == 0.5 ~ "site 3",
    group == 0.75 ~ "site 4",
    group == 0.99 ~ "site 5"
  )]

# /*--------------------------------*/
#' ## Visualization
# /*--------------------------------*/
sub_dt <- res_y_dt[variable == "Yield" & N == opt_N]

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist
```


# Illustrative Examples of Yield Response Curves Estimated by RF and BRF (Figure 7)


```{r prepare-data-vis, cache = TRUE}
# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- ML functions --- #
library(grf)
source(here("Codes/0_2_functions_main_sim.R"))

# --- Data --- #
test_subplot_dt <- 
  here("Data/for_writing/field_subplot_test_dt.rds") %>%
  readRDS()

# /*===== Train ML =====*/
temp_var_ls <-
  c(
    "alpha1", "alpha2", "beta1", "beta2", "ymax1",
    "ymax2", "theta_1", "theta_2"
  )

set.seed(1356)

RF <-
  RF_run(
    reg_data = data.table(field_subplot_sf),
    var_ls = temp_var_ls
  )

BRF <-
  BRF_run(
    reg_data = data.table(field_subplot_sf),
    var_ls = temp_var_ls
  )

# /*===== Yield Calculation =====*/
# --- All N experimental rates --- #
N_rate <- test_subplot_dt[, aa_n] %>% unique() %>% sort()

# --- for true yield response function --- #
seq_N <-
  seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)

res_true <-
  test_subplot_dt %>%
  # .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = unique_subplot_id] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)]

# --- for predicted yield at five experimental N rates --- #
res_pred <-
  test_subplot_dt %>%
  # .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)), ] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[, RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  # .[cnn_pred, on = c("sim", "unique_subplot_id", "N")] %>%
  melt(
    id.vars = c("unique_subplot_id", "yield", "aa_n", "N"),
    # measure.vars = c("RF", "BRF", "CNN")
    measure.vars = c("RF", "BRF")
    ) %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed",
    "Unobserved"
  )] %>%
  .[, y_diff := abs(yield - value)]


# /*===== Preparation for plots =====*/
vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")]

vis_res_pred <-
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, type := "Predicted"] %>%
  setnames("variable", "model") %>%
  .[, .(N, value, type, observed, model, unique_subplot_id)]

vis_true_points <-
  vis_res_true %>%
  .[N %in% unique(vis_res_pred$N), ] %>%
  .[, type := "True"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("yield", "value") %>%
  .[rep(1:.N, 2), ] %>%
  .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
  .[, .(N, value, type, observed, model, unique_subplot_id)]

vis_all_points <- rbind(vis_res_pred, vis_true_points)
```

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = unique_subplot_id)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = unique_subplot_id),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  annotate(
    "text",
    x = 180, y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```


# Field Maps

## Division of Field: plots, subplots and cells (Figure 1)

```{r field-map-visualization, dependson = "setup"}
# === Preparation === #
ex_plot <- field_plot_sf[224, ]
ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]

ex_one_subplot <- ex_subplots[1, ]
ex_cells <- field_cell_sf[ex_one_subplot, , op = st_within]


one_subplot <- ex_subplots[3, ]

#-- (1) plot-level field map  --#
plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("12 \u00D7 32 plots") +
  theme_figure


grob_plot <- ggplotGrob(plot)

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <-
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2, ], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

grob_subplots_inPlot <- ggplotGrob(subplots_inPlot)

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2, ], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

grob_cells_inSubplot <- ggplotGrob(cells_inSubplot)

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
  ) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7
  ) +
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8 + 0.2, ymin = 0.382, ymax = 0.382 + 0.2
  ) +
  # /*----------------------------------*/
  #' ## Add braces
  # /*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43, 0.43 + 0.1), c(0.372 - 0.004, 0.645 + 0.013)), color = "red", rotate = 270, inherit.data = F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401 - 0.002, 0.529 + 0.011)), color = "red", rotate = 270, inherit.data = F) +
  # /*----------------------------------*/
  #' ## add annotations
  # /*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family = "Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family = "Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family = "Times New Roman") +
  theme_void()
```

## Experimental N Design (Figure 3 Left)

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  ggtitle("(1) Trial design") +
  theme_figure
```


## Yield Map (Figure 3 Right)

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield level\n  (kg/ha)") +
  ggtitle("(2) Simulated yield level") +
  theme_figure
```


## Field Characteristics Map (Appendix: Figure C.1)

```{r, dependson = "setup"}
# === alpha map === #
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(1) " ~ alpha)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === beta map === #
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(2) " ~ beta)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === ymax map === #
field_ymax <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = ymax), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(3) ymax (kg/ha)") +
  theme(legend.title = element_blank()) +
  theme_figure

# === m_error map === #
field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression(paste("(4) " ~ epsilon, " (kg/ha)"))) +
  theme(legend.title = element_blank()) +
  theme_figure

# === optN map === #
field_optN <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = opt_N), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(5) EONR (kg/ha)") +
  theme(legend.title = element_blank()) +
  theme_figure
```

## Low and High Yield Error Maps (Appendix: Figure G.1)

```{r}
# === Low error field map === #
field_cell_low_sf <-
  here("Data/for_writing/sample_field_cell_low_sf.rds") %>%
  readRDS()

field_m_error_low <-
  ggplot(field_cell_low_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
  ggtitle("(1) Low error") +
  theme_figure

# === High error field map === #
field_cell_high_sf <-
  here("Data/for_writing/sample_field_cell_high_sf.rds") %>%
  readRDS()

field_m_error_high <-
  ggplot(field_cell_high_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
  ggtitle("(2) High error") +
  theme_figure
```


# Simulation Results

## Load the Results

```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
# === Load Results === #
allML_summary_bySim <- readRDS(here("Data/for_writing/allML_summary_bySim.rds"))

# === Set up === #
res_y_train <-
  allML_summary_bySim %>%
  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]

res_y_test <-
  allML_summary_bySim %>%
  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
```


# Yield Prediction Results from the Main Simulations

## Summary Table for RMSE of of Yield Prediction

### on Training Datasets (Appendix: Table F.2)

```{r, dependson = "source-results"}
# /*===== On training datasets =====*/
report_table_y_train <-
  res_y_train %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

### on Testing Datasets (Table 2)

```{r, dependson = "source-results"}
# --- on testing data sets--- #
report_table_y <-
  res_y_test %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```


## The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario (Figure 8)

```{r}
sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist +
  labs(fill = "Simulation Round", shape = "Method") +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  labs(fill = "Simulation Round", shape = "Method")
```



## True Yields without Error vs Predicted Yields (Appendix: Figure E.1)


```{r}
sample_simRes_test_y <- readRDS(here("Data/for_writing/sample_simRes_test_y.rds"))

# === Function for RMSE Calculation === #
rmse_general <- function(preds, actual) {
  sqrt(mean((actual - preds)^2)) %>%
    round(., 1) %>%
    format(, nsmall = 1)
}

rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = rmse_general(pred_yield, det_yield),
    rmse_y = rmse_general(pred_yield, yield)
  ), by = .(Method, Model)]


rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = paste0("RMSE = ", rmse_general(pred_yield, det_yield)),
    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
  ), by = .(Method, Model)]


vis_y_pred <-
  ggplot(sample_simRes_test_y) +
  geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  geom_text(
    data = rmse, aes(x = -Inf, y = +Inf, label = rmse_y_det),
    hjust = -0.1, vjust = 3, size = 3.5, family = "Times New Roman"
  ) +
  facet_grid(Model ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Predicted Yield (kg/ha)") +
  labs(x = "True Yield without error (kg/ha)") +
  theme_dist
```




## Yield Prediction vs EONR estimation : Count Table in terms of profit loss (Table 3)

```{r, dependson = "source-results"}
# === Preparation === #
prepare_count_tab <-
  res_y_test %>%
  dcast(sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
  .[, which_ML_y := case_when(
    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
  )] %>%
  .[, which_ML_piLoss := case_when(
    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
  )] %>%
  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)]

# === Summary Table === #
summary_res_CNN_RF_BRF <-
  prepare_count_tab %>%
  .[, .(
    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
    Total = sum(index_cnst_y_piLoss)
  ), by = Model] %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.8) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```


# EONR Estimation from the Main Simulations

## Distributions of RMSE of EONR estimation over simulations (Figure 4)

```{r, dependson = "source-results"}
# /*----------------------------------*/
#' ## Distribution of RMSE of EONR estimates
# /*----------------------------------*/
plot_dis_optN <-
  allML_summary_bySim %>%
  .[type == "test", ] %>%
  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  facet_wrap(~Model, ncol = 1) +
  labs(x = "RMSE (kg/ha)") +
  theme_dist

```

## Summary Table for RMSE of EONR estimation

### on Training Datasets (Appendix: Table F.1)

```{r, dependson = "source-results"}
# /*----------------------------------*/
#' ## Summary Table
# /*----------------------------------*/
# === Preparation === #
table_optN_prep <-
  allML_summary_bySim %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]


# === Summary Table (Training Data sets) === #
report_table_optN_train <-
  table_optN_prep %>%
  .[type == "train", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)

```

### on Testing Datasets (Table 1)

```{r, dependson = "source-results"}
# === Summary Table (Testing Data sets) === #
report_table_optN <-
  table_optN_prep %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```


## Distributions of profit deficit over simulations (Figure 5)

```{r}
piLoss_density <-
  allML_summary_bySim %>%
  .[type == "test", ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist
```

## Treatment effect comparison (Figure 6)

```{r}
figure_te <-
  here("Data/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  ggplot() +
  geom_point(aes(x = true_te_base, y = te_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_dist
```

# Appendix

## Variogram Prameter Table (Appendix: Table C.1)

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(-0.5, format(0), 12000, format(0)),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(0.02, format(1, nsmall = 1), 2000000, 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sub(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sub(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
  # compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph("r", as_sup(as_i(" \U03B5")), as_sub(as_i("i,j")))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 3, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 3, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"), ")."),
    ref_symbols = NA
  ) %>%
  # set_caption(
  #   caption = "Table C.1: The parameters for the Variogram models",
  #   style = "Table Caption"
  # ) %>%
  autofit()
```



## An Example of a Causal Tree (Appendix: Figure A.1)

```{r, cache = TRUE}
# /*=================================================*/
#' # Sample CT figure
# /*=================================================*/
library(causalTree)
library(rattle)

data_dt <- readRDS(here("Data/ctree_data.rds"))

tgts_ls <- data_dt[, tgts] %>%
  unique() %>%
  sort()

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2], ] %>%
  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[, yield := yield * 62.77]

tree <- causalTree(
  yield ~ slope + ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
# par(family = "Times")
# fancyRpartPlot(opfit, sub = "")
```

## Various Error Size - EONR Estimation (Appendix: Table G.1)

```{r, cache = F}
# === Load the data === #
Simres_low <-
  here("Data/for_writing/allML_summary_bySim_low.rds") %>%
  readRDS()

Simres_high <-
  here("Data/for_writing/allML_summary_bySim_high.rds") %>%
  readRDS()

Simres_low_high <-
  bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
  .[, Degree := ifelse(Degree == 1, "Low", "High")] %>%
  .[, Degree := factor(Degree, levels = c("Low", "High"))] %>%
  .[type == "test", ]


# === Preparation === #
table_optN_prep_low_high <-
  Simres_low_high %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(Degree, Method, Model)] %>%
  dcast(Degree + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Degree, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]


# === Summary Table (Testing Data sets) === #
table_optN_low_high <-
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 7, 10, 13), width = 0.6) %>%
  width(j = c(5, 8, 11, 14), width = 0.5) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)
```


## Various Error Size - Yield Prediction (Appendix: Table G.2)

```{r}
# /*--------------------------------*/
#' ## Yield prediction
# /*--------------------------------*/
report_table_y_low_high <-
  Simres_low_high %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.82) %>%
  align(j = 2, align = "left", part = "body")
```


## Yield Prediction vs EONR estimation : Count Table in terms of profit loss

```{r, dependson = "source-results"}
# === Preparation === #
prepare_count_tbl_low_high <-
  Simres_low_high %>%
  .[Method %in% c("RF", "BRF", "CNN")] %>%
  dcast(Degree + sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
  .[, which_ML_y := case_when(
    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
  )] %>%
  .[, which_ML_piLoss := case_when(
    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
  )] %>%
  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)] %>%
  .[, .(
    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
    Total = sum(index_cnst_y_piLoss)
  ), by = .(Degree, Model)] %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Degree, Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]

# === Table creation === #
count_tbl_low_high <-
  prepare_count_tbl_low_high %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4:5, 7:8, 10:11), width = 0.5) %>%
  width(j = 13, width = 0.82) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)
```
